papers

### 2021-09-29 index.Rmd
adding functionality

# THIS IS A TEST SITE

## Researcher, Open Science Enthusiast, Lovable Bawbag

My name is Sam Parsons. I’m a Postdoctoral Research Associate in the Department of in Experimental Psychology at Oxford University. I work in the Oxford Centre for Emotion and Affective Neuroscience, aka OCEAN. Just in case you’re here for the cat, this ginger monster is called Beau.

As well as investigating cognitive-affective processes implicated in adolescent worry, I try to do my own small bit for the improvement of psychological science. Sometimes this is promoting open and reproducible research practices; others it is frustrating others by highlighting the importance of routinely estimating and reporting the reliability of our measurements. Mostly, I’d just like us all to get along and do good research.

@@

(I try to keep this website up to date, however it may fall slightly behind. I do keep my CV up to date, so please do refer to that)

@@

![splithalf package hexlogo](splithalf.png)

>>>>

I’m a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow. I work in the [Lifespan Cognitive Dynamics Lab](https://www.rogierkievit.com/) based at the [Donders Institute](https://www.ru.nl/donders/). I did my DPhil in Experimental Psychology at the University of Oxford (a DPhil is a PhD but of course they need to call it something else)

Just in case you’re here for the cat, this ginger monster is called Beau.

Radboud project

Open Scholarship - ReproducibiliTea and FORRT

I try to do my own small bit for the improvement of psychological science. Sometimes this is promoting open and reproducible research practices; others it is frustrating others by highlighting the importance of routinely estimating and reporting the reliability of our measurements. Mostly, I’d just like us all to get along and do good research.

Previous projects & talks

Seriousness - not a huge fan

@@

(I try to keep this website up to date, however it may fall slightly behind. I do keep my [CV](Sam_Parsons_cv.pdf) up to date, so please do refer to that)

@@

![](splithalf.png)

### 2021-09-29 papers.Rmd
mini update papers
adding functionality

aside_center <- function(text) {
  return(aside(center(list(text))))
}
```

@@

@@

>>>>

```

@@

<div data-badge-type="donut" data-doi="10.1080/02699931.2021.1915752" data-hide-no-mentions="true" class="altmetric-embed"></div>

@@

<div data-badge-type="donut" data-doi="10.1177/2515245919879695" data-hide-no-mentions="true" class="altmetric-embed"></div>
